
  \begin{thebibliography}{99}
\bibitem{Altshuler1}Altshuler, B. \& A. G. Aronov Zero bias anomaly in tunnel resistance and electron-electron interaction. {\em Solid State Communications}. \textbf{30} pp. 115-117 (1979)
\bibitem{Altshuler3}Altshuler, B. \& A. G. Aronov Fermi-liquid theory of the electron-electron interaction effects in disordered metals. {\em Solid State Communications}. \textbf{46} pp. 429-435 (1983)
\bibitem{Altshuler4}Altshuler, B. \& A. G. Aronov Electron-Electron Interactions in Disordered Systems. (Elsevier,1985)
\bibitem{Abeles}Abeles, B., Sheng, P., Coutts, M. \& Y. Arie Structural and electrical properties of granular metal films. {\em Advances In Physics}. \textbf{24} pp. 407-461 (1975)
\bibitem{Dynes}Dynes, R. \& J. P. Garno Metal-Insulator Transition in Granular Aluminum. {\em Physical Review Letters}. \textbf{46} pp. 137-140 (1981)
\bibitem{McMillan2}McMillan, W. \& J. Mochel Electron Tunneling Experiments on Amorphous Ge1-xAux. {\em Physical Review Letters}. \textbf{46} pp. 556-557 (1981)
\bibitem{ImryOvadyahu}Imry, Y. \& Z. Ovadyahu Density-of-States Anomalies in a Disordered Conductor: A Tunneling Study. {\em Physical Review Letters}. \textbf{49} pp. 841-844 (1982)
\bibitem{Schmitz1}Schmitz, S. \& S. Ewert Electron density of states anomalies in disordered gold, silver and indium films. {\em Solid State Communications}. \textbf{74} pp. 1067-1070 (1990)
\bibitem{Schmitz2}Schmitz, S. \& S. Ewert Electron tunneling experiments on amorphous $Ti_xTe_{1-x}$ films. {\em Solid State Communications}. \textbf{79} pp. 525-529 (1991)
\bibitem{Escudero}Escudero, R., Lasjaunias, J., Calvayrac, Y. \& M. Boudard Tunnelling and point contact spectroscopy of the density of states in quasicrystalline alloys. {\em Journal Of Physics: Condensed Matter}. \textbf{11} pp. 383-404 (1999)
\bibitem{Teizer}Teizer, W., Hellman, F. \& R. C. Dynes Density of States of Amorphous $Gd_xSi_{1-x}$ at the Metal-Insulator Transition. {\em Physical Review Letters}. \textbf{85} pp. 848-851 (2000)
\bibitem{Mazur}Mazur, D., Gray, K., Zasadzinski, J., Ozyuzer, L., Beloborodov, I., Zheng, H. \& J. F. Mitchel Redistribution of the density of states due to Coulomb interactions in $La_{2-x}Sr_{1+2x}Mn_2O_7$. {\em Physical Review B}. \textbf{76} pp. 193102-1-4 (2007)
\bibitem{Luna2014}Luna, K., Giraldo-Gallo, P., Geballe, T., Fisher, I. \& M. Beasley Disorder Driven Metal-Insulator Transition in $BaPb_{1-x}Bi_xO_3$ and Inference of Disorder-Free Critical Temperature. {\em Physical Review Letters}. \textbf{113} pp. 177004-1-5 (2014)
\bibitem{Luna2015}Luna, K., Wu, P., Chen, J., Morosan, E. \& M. Beasley Point-contact tunneling spectroscopy measurement of $Cu_xTiSe_2$: Disorder-enhanced Coulomb effects. {\em Physical Review B}. \textbf{91} pp. 094509-1-4 (2015)
\bibitem{Kobayashi}Kobayashi, M., Tanaka, K., Fujimori, A., Ray, S. \& D. D. Sarma Critical Test for Altshuler-Aronov Theory: Evolution of the Density of States Singularity in Double Perovskite $Sr_2FeMoO_6$ with Controlled Disorder. {\em Physical Review Letters}. \textbf{98} pp. 246401-1-4 (2007)
\bibitem{LeeRamakrishnan}Lee, P. \& T. V. Ramakrishnan Disordered electronic systems. {\em Reviews Of Modern Physics}. \textbf{57} pp. 287-337 (1985)
\bibitem{Imry}Imry, Y. Introduction to Mesoscopic Physics. (Oxford University Press,2002)
\bibitem{Rabatin}Rabatin, B., Superconductivity in systems with weakly screened Coulomb interactions. (Master thesis, Comenius University Bratislava,2017)
\bibitem{Hlubina}Rabatin, B., Hlubina, R.,  Superconductivity in systems exhibiting the Altshuler-Aronov anomaly. {\em Physical Review B}.  \textbf{98} pp. 184519-1-10 (2018)
\bibitem{Mermin}Mermin N.W, N. Solid State Physics. (Cengage Learning,1976)
\bibitem{Moskova} Mošková, A., Moško, M.,  States-conserving density of states for Altshuler-Aronov effect: Heuristic derivation. {\em Solid State Communications  }  \textbf{284-286}   pp. 56 (2018)
\bibitem{Thouless} Thouless D.J.,  Relation between the Kubo-Greenwood formula and the Boltzmann equation for electrical conductivity, {\em Philosophical Magazine } \textbf{32:4}  pp. 877-879    (1975)
\bibitem{Bakalarka} Jenča M., Vplyv elektrón-elektrónovej interakcie a disorderu na hustotu stavov v kove: Teoretické skúmanie (Bakalárska práca, Univerzita Komenského v Bratislave, 2019)
\bibitem{Kubo} Kubo R.,  The fluctuation-dissipation theorem,   {\em Reports on progress in physics } \textbf{29.1} pp.255  (1966)
\bibitem{Mello} Mello, P. A., and Kumar N., Quantum Transport in Mesoscopic Systems: Complexity and Statistical Fluctuations. A Maximum Entropy Viewpoint. Oxford: Oxford University Press, 2004. 
\end{thebibliography}